TBD

### 2020-11-01 outputs/paper/paper.Rmd
Update paper.Rmd

- 76 different ages;
- 11 education levels
- 15 races;
- 24 income levels;
- 51 states
- 2 options for mask wearing habits.

@@

```{r, eval = FALSE}
fit <- brms::brm(
  binary ~ (1 | state) + (1 | age) + (1 | education) + (1 | household_income),
  family = bernoulli(link = "logit"),
  data = clean_survey
)
print(fit)
```

>>>>

- 76 different ages;
- 11 education levels
- 15 races;
- 24 income levels;
- 51 states;
- 2 options for mask wearing habits.

@@

```{r}
fit <- brms::brm(
  binary ~ (1 | age) + (1 | education) + (1 | race_ethnicity0)+ (1 | hispanic)
  + (1 | household_income) + (1 | state) + (1 | extra_covid_worn_mask),
  family = bernoulli(link = "logit"),
  data = clean_survey
)
print(fit)
```
